### 2014-06-28 Choosing R3 Relations.tex
small_square_commuting_relations_edit

\begin{rem}
I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$
\end{rem}

\begin{lem}
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

>>>>

\begin{rem}
I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$ It seems the additional relation is in fact preserved under mutations of type b or c, as in Barot and Marsh's classification. However, I couldn't get type d to work out. I think we may have to add some of these types of relations  $s_as_as_b = s_bs_as_a$ when there are 2's around, such that the mutation in d works out.
\end{rem}

\begin{lem} (4.2 Analog)
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}
